### 2019-09-28 main.tex
updates management
adds letter, moves title text up
adds gavin bio
general updates
New usepackages
updates main
changes the header to block I
changes title
updates org chart

\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{eso-pic}
\usepackage{soul}
\usepackage{xcolor}
\usepackage[parfill]{parskip}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography
\usepackage[toc,page]{appendix} % creates an appendix
\usepackage{fancyhdr}
% \usepackage{pagecounting}
% \usepackage[dvips]{color}

\newcommand{\illinoislogo}{\includegraphics[height=0.5in]{images/illinoislogo.png}}
\newcommand{\anslogo}{\hspace{-4mm}\includegraphics[height=0.5in]{images/ansuiuc.png}}
\newcommand{\anssite}{ans.npre.illinois.edu}
% \usepackage{background}
\usepackage{float}
\usepackage[top=2cm, bottom=2.75cm, outer=2cm, inner=2cm]{geometry}
\setcounter{tocdepth}{3}
% \setcounter{secnumdepth}{3}
\usepackage{environ}
\NewEnviron{letter}{%
  \input{structure}
  \opening
  \closing
}

@@

\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
% \tikzstyle{arrow} = [thick,--,>=stealth]

\begin{document}
% ======================================================================================================
% DO NOT EDIT THIS SECTION
% ======================================================================================================
\begin{titlepage}
\AddToShipoutPictureBG*{\includegraphics[angle=90, width=\paperwidth,height=\paperheight]{earth1.png}};

@@

       \vspace*{0.25cm}

@@

       \vspace{0.3cm}
       Nuclear, Plasma, and Radiological Engineering

       \vfill
       \vspace{7.5cm}

@@

\pagestyle{fancy}
\lhead{\anslogo}
\rhead{\illinoislogo}

\input{letter}

@@

\input{theme}
\newpage
\input{uiuc}
\newpage
\input{conflog}
\newpage
\input{proglog}
\newpage
\input{management}
\newpage
\input{website}
\newpage
\input{budget}
\newpage
\input{liability}
\newpage
% Appendices
\appendix
\input{conflict}
\input{judging}
\input{schedule}
\input{building}
\input{locations}
\input{staffreq}
\input{facultyletter}
\input{petition}

>>>>

\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{wrapfig}
\usepackage{eso-pic}
\usepackage{soul}
\usepackage{xcolor}
\usepackage[parfill]{parskip}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
\usepackage{microtype} % Improves typography
\usepackage[toc,page]{appendix} % creates an appendix
\usepackage{fancyhdr}
\usepackage{pdfpages}
\usepackage{multirow}
\usepackage{array}
% \usepackage{pagecounting}
% \usepackage[dvips]{color}
\newcommand{\STAB}[1]{\begin{tabular}{@{}c@{}}#1\end{tabular}}
\newcommand{\illinoislogo}{\includegraphics[height=0.5in]{images/block-I.png}}
\newcommand{\anslogo}{\hspace{-4mm}\includegraphics[height=0.5in]{images/ansuiuc.png}}
\newcommand{\anssite}{ans.npre.illinois.edu}
% \usepackage{background}
\usepackage{float}
\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
\setcounter{tocdepth}{3}
% \setcounter{secnumdepth}{3}
\usepackage{environ}
\NewEnviron{letter}{%
  \input{structure}
  \opening
  \closing
}

@@

\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{3.5cm}},execute at end node={\end{varwidth}}]
\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{3.5cm}},execute at end node={\end{varwidth}}]
\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{3.5cm}},execute at end node={\end{varwidth}}]
% \tikzstyle{arrow} = [thick,--,>=stealth]

\begin{document}
% ======================================================================================================
% DO NOT EDIT THIS SECTION
% ======================================================================================================
\begin{titlepage}
\AddToShipoutPictureBG*{\includegraphics[angle=90,width=\paperwidth,height=\paperheight]{earth1.png}}

@@

       % \vspace{0.15cm}

@@

       % \vspace{0.1cm}
       % Nuclear, Plasma, and Radiological Engineering
       % \includegraphics[width=0.4\textwidth]{ans_sc_logo3.png}

       \vfill
       \vspace{8.5cm}

@@

\setlength{\headheight}{25pt}
\pagestyle{fancy}
\lhead{\anslogo}
\rhead{\illinoislogo}
% \renewcommand{\headrulewidth}{0pt} % no line in header area
% \fancyhead{}

\includepdf[pages=-]{./documents/chair_letter.pdf}

@@

\input{theme}
\newpage
\input{uiuc}
\newpage
\input{conflog}
\input{proglog}
\newpage
\input{management}
\newpage
\input{website}
\newpage
\input{budget}
% \newpage
\input{liability}
\newpage
% Appendices
\appendix
\input{conflict}
\input{judging}
\input{schedule}
\input{building}
\input{locations}
\input{staffreq}
\input{facultyletter}
\input{petition}

### 2019-09-28 management.tex
updates org chart

		\node (log chair) [director, below of = gen chair, xshift = -2.5cm, yshift = -2cm] {Logistics Chair (Natalie Gaughan)};
		\node (med coord) [coordinator, below of = gen chair, xshift = 1cm, yshift = -4cm] {Media Coordinator (Nathan Ryan)};
		\node (prog coord) [coordinator, below of = log chair, yshift = -2cm] {Program Coordinator (Dilan K.)};
		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations (Brady Moran)};
		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Anna Balla)};

		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator (Roberto Fairhurst)};
		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};

		\node (fin chair) [director, below of = tech chair, xshift = -2cm, yshift = -2cm] {Financial Chair (Jack Stahl)};
		\node (spon coord) [coordinator, below of = fin chair, yshift = -2cm] {Sponsorships Coordinator (Jimmy Shehee)};
		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator (Jasmine Dinari)};

>>>>

		\node (log chair) [director, below of = gen chair, xshift = -3.75cm, yshift = -2cm] {Logistics Chair\\ (Natalie Gaughan)};
		\node (med coord) [coordinator, below of = gen chair, xshift = 0.0cm, yshift = -3cm] {Media Coordinator (Nathan Ryan)};
		\node (prog coord) [coordinator, below of = log chair, yshift = -2cm] {Program Coordinator (Dilan K.)};
		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations\\ (Brady Moran)};
		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Anna Balla)};

		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};

		\node (fin chair) [director, below of = tech chair, xshift = -2.25cm, yshift = -2cm] {Financial Chair\\(Jack Stahl)};
		\node (spon coord) [coordinator, below of = fin chair, yshift = -2cm] {Sponsorships Coordinator (Jimmy Shehee)};
		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator\\(Jasmine Dinari)};
